\documentclass[12pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage[maxcitenames=6, minnames=3 ]{biblatex}
\addbibresource[]{biblio.bib}

% bold the name of specific author
\usepackage{xstring}
\usepackage{etoolbox}
\newboolean{bold}
\newcommand{\makeauthorsbold}[1]{%
  \DeclareNameFormat{author}{%
  \setboolean{bold}{false}%
    \renewcommand{\do}[1]{\expandafter\ifstrequal\expandafter{\namepartfamily}{####1}{\setboolean{bold}{true}}{}}%
    \docsvlist{#1}%
    \ifthenelse{\value{listcount}=1}
    {%
      {\expandafter\ifthenelse{\boolean{bold}}{\mkbibbold{\namepartfamily\addcomma\addspace \namepartgiveni}}{\namepartfamily\addcomma\addspace \namepartgiveni}}%
    }{\ifnumless{\value{listcount}}{\value{liststop}}
      {\expandafter\ifthenelse{\boolean{bold}}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}%
      {\expandafter\ifthenelse{\boolean{bold}}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}%
      }
    \ifthenelse{\value{listcount}<\value{liststop}}
    {\addcomma\space}{}
  }
}
\makeauthorsbold{Farah, Irene}

% what is your name?
\newcommand{\myname}{Irene Farah}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.8}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {Urban Politics, Informality, Food Systems, Methods},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    % \nobibliography*
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        PhD Candidate \\
        Department of City and Regional Science \\
        University of California, Berkeley
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:irenef@berkeley.edu}{irenef@berkeley.edu} \\
        +1 773 717 3517 \\
        \href{https://ifarah.github.io}{ifarah.github.io}\\
        %\href{https://orcid.org/0000-0003-0227-9896}{orcid:0000-0003-0227-9896}
    \end{minipage}

    \section*{Education}
    
    \begin{tablist}
      \item[Ph.D.] \tab{}City \& Regional Planning, University of California, Berkeley, USA, 2019-2024 \\
      %\color{red}
      %\extrasmall{Committee: Daniel Rodríguez (co‑chair), Alison Post (co‑chair), and Carolina Reid}
%\color{black}
      \item[M.A.] \tab{}Social Sciences, University of Chicago, Illinois, USA, 2016-2017
      \item[B.A.] \tab{}Political Science, Instituto Tecnológico Autónomo de México, Mexico City, Mexico, 2009-2013
    \end{tablist}
    
    \section*{Research Areas}
    \begin{itemize}
\item My research focuses on \textbf{urban politics, informality, food systems,} and \textbf{methods}.

\subitem \textbf{Urban Politics:} How regulations and the intermediation between local governments and street \\
\hspace{1.5em} vendors impact how public space is assigned and contested in Mexico City and San Francisco.

\subitem \textbf{Food Systems:} The role of informal outlets in Mexico's food environment. \\
\hspace{1.5em} food environments.

\subitem \textbf{Methods:}  Mobility of street vendors through location-based data, point pattern analyses of retail\\
\hspace{1.5em} data, spatial accessibility metrics,  mathematical demography to examine firm dynamics, analyzing \\
\hspace{1.5em} heat waves through remote sensing. 
    \end{itemize}
    
    \section*{Research Experience}
    \begin{tablist}
        \item[2019‐2020] \quad{}Graduate Researcher, Institute of Urban and Regional Development, UC Berkeley
        \item[2016‐2019] \quad{}Research Associate, Center for Spatial Data Science, University of Chicago
        \item[2014‐2015] \quad{}Research Advisor, National Council for the Evaluation of Social Development Policy \\
        \hspace{1em}(CONEVAL), Mexico City
    \end{tablist}

    \section*{Publications}
    \subsection*{Journal Articles}
    \begin{tablist}
        \item[2024] \tab{}\fullcite{diss}
        \item[2023] \tab{}\fullcite{bmc2023} 
        \item[2023] \tab{}\fullcite{heat2023}
        \item[2023] \tab{}\fullcite{frontiers}
        \item[2022] \tab{}\fullcite{phn} 
    \end{tablist}

    \subsection*{Book Chapters}
    \begin{tablist}  
        \item[2023] \tab{}\fullcite{anselinretail}
        \item[2023] \tab{}\fullcite{kevinretail}
    \end{tablist}

    \subsection*{Book Reviews and Miscellanea}
    \begin{tablist}  
        \item[2021] \tab{}\fullcite{holland2021}
        \item[2019] \tab{}\fullcite{access2019}
        \item[2018] \tab{}\fullcite{meth2018}
    \end{tablist}


    \section*{Teaching}
    \subsection*{University of California, Berkeley}
    \begin{tablist}
        \item[2022] \tab{}$\>$ $\>$ $\>$ Planning Methods Gateway: Part I (graduate), Graduate Student Instructor.
        \item[2022] \tab{}$\>$ $\>$ $\>$ Maps as Social Justice Interventions, Instructor and created course with Karen Chapple.
        \item[2021, 2022] $\>$ $\>$  R Geospatial and US Census, Workshops. D‐Lab.
        \item[2020, 2022] $\>$ $\>$  Urban Informatics and Visualization (graduate), Graduate Student Instructor.
        \item[2021] \tab{} $\>$ $\>$ $\>$  Introduction to City Planning, Graduate Student Instructor.
        \item[2021] \tab{} $\>$ $\>$ $\>$  Introduction to Urban Data Analytics, Graduate Student Instructor.
    \end{tablist}
    
    \subsection*{Colegio de México}
        \begin{tablist}
        \item[2023, 2022] $\>$ $\>$Introduction to Spatial Econometrics (graduate, in Spanish).
    \end{tablist}


    \section*{Awards}
    \subsection*{Awards and Honors}
    \begin{tablist}
        \item[2024] \quad{}Political Economy Network Fellow, Network for a New Political Economy, UC Berkeley 
        \item[2023] \quad{}Graduate Student Fellow, Institute for the Study of Societal Issues, UC Berkeley
        \item[2022] \quad{}Outstanding Graduate Student Instructor Award, UC Berkeley
        \item[2022] \quad{}Michael B. Teitz Fellowship, UC Berkeley 
        \item[2021] \quad{}Graduate Student Fellow, Berkeley Food Institute, UC Berkeley
        \item[2021] \quad{}Graduate Student Fellow, D‐Lab, UC Berkeley
        \item[2021] \quad{}Tinker Field Research Grant, CLAS, UC Berkeley
        \item[2020] \quad{}Summer Research Grant, Global Metropolitan Studies, UC Berkeley
        \item[2019] \quad{}Outstanding Reviewer, Housing Policy Debate
        \item[2016] \quad{}Fellowship, University of Chicago
        \item[2015] \quad{}Award \textit{La Flecha Al Aire} for BA thesis on education, ITAM
        \item[2013] \quad{}Scholarship on Social Mobility Research, Centro de Estudios Espinosa Yglesias (CEEY), Mexico
    \end{tablist}
    

    %\subsection*{Conference Proceedings}
    %\begin{tablist}
    %    \item[2022] \tab{}\fullcite{luo2022abode-net}
    %    \item[2021] \tab{}\fullcite{li2021deep}
    %\end{tablist}

    % \section*{INVITED TALKS}
    % \subsection*{Campus Talks}

    \section*{Selected Presentations}
    \small{(*) = Invited} \\

    \begin{tablist}
        \item[2024] \tab{}\fullcite{uaa2024}
        \item[2023*] \tab{}\fullcite{scramblemich}
        \item[2023] \tab{}\fullcite{apsaluskin2023}
        \item[2023] \tab{}\fullcite{acsp2023}
        \item[2023] \tab{}\fullcite{mov2023}
        \item[2023] \tab{}\fullcite{uaa2023}
        \item[2022] \tab{}\fullcite{acsp2022}
        \item[2022] \tab{}\fullcite{apsa2022}
        \item[2020] \tab{}\fullcite{acsp2020}
        \item[2019] \tab{}\fullcite{aag2019}
        \item[2019] \tab{}\fullcite{wrsa2019}
        \item[2018] \tab{}\fullcite{narsc2018}
        \item[2015] \tab{}\fullcite{hdca2015}
    \end{tablist}


    
    
    %\section*{Conference Activity}
    %\begin{tablist}
    %    \item[2022] \tab{}The 7th International Conference on Smart Computing and Communication (SmartCom 2022), New York, USA
    %    \item[2022] \tab{}NSF EPSCoR Workshop on Artificial Intelligence \& No-Boundary Thinking, Little Rock, Arkansa
    %\end{tablist}

%    \section*{Awards}
%    \subsection*{Awards and Honors}
%    \begin{tablist}
%        \item[2023‐2024] $\>$  $\>$ Political Economy Network Fellow, Network for a New Political Economy, UC Berkeley 
%        \item[2022‐2023] $\>$ $\>$  Graduate Student Fellow, Institute for the Study of Societal Issues, UC Berkeley
%        \item[2022     ] \tab{}$\>$$\>$ $\>$  Outstanding Graduate Student Instructor Award, UC Berkeley
%        \item[2022     ] \tab{}$\>$ $\>$   Michael B. Teitz Fellowship, UC Berkeley 
%        \item[2021‐2022] $\>$ $\>$  Graduate Student Fellow, Berkeley Food Institute, UC Berkeley
%        \item[2021‐2022] $\>$ $\>$ Graduate Student Fellow, D‐Lab, UC Berkeley
%        \item[2021     ] \tab{}$\>$$\>$ $\>$  Tinker Field Research Grant, CLAS, UC Berkeley
%        \item[2020     ] \tab{}$\>$ $\>$ $\>$ Summer Research Grant, Global Metropolitan Studies, UC Berkeley
%        \item[2019     ] \tab{}$\>$$\>$ $\>$  Outstanding Reviewer, Housing Policy Debate
%        \item[2016     ] \tab{}$\>$$\>$ $\>$  Fellowship, University of Chicago
%        \item[2013     ] \tab{}$\>$$\>$  $\>$ Award La Flecha Al Aire for BA thesis on education,
%        \item[2013     ] \tab{}$\>$ $\>$  Scholarship on Social Mobility Research, Centro de Estudios Espinosa Yglesias
%    \end{tablist}


    \section*{Academic Service}
    \subsection*{Sessions Organized}
    \begin{tablist}
        \item[2024] \tab{}Co-organizer: Housing and Land Regulations in the Political Economy of Urban Latin America. Five sessions. \textbf{Association of Collegiate Schools of Planning}, Seattle, Washington (with Flávia Leite).
        \item[2024] \tab{}Co-organizer: Urban Governance of Informal Work: Perspectives Across the North-South Divide. Five sessions. \textbf{Urban Affairs Association}, New York City, New York (with Ryan Devlin).
        \item[2023] \tab{}Organizer: Computational Approaches to Urban Planning and Management: Innovations and Challenges. Four sessions.  \textbf{Association of Collegiate Schools of Planning}, Chicago, Illinois.
        \item[2023] \tab{}Co-organizer: Informal Work and Public Space during COVID-19. Five sessions. \textbf{Urban Affairs Association}, Nashville, Tennessee (with Ryan Devlin)
    \end{tablist}

    \subsection*{Manuscript Reviewer}
    Berkeley Planning Journal (co‑editor 2021‑2022); Environment and Planning B: Urban Analytics and City Science; Regional Studies, Regional Science; Food Security; Journal of Urbanism: International Research on Placemaking and Urban Sustainability; Journal of Planning Education and Research; Housing Policy Debate; Transportation Review Board; Geographical Analysis

    \subsection*{Memberships}
Association of Collegiate Schools of Planning (ACSP)\\
Urban Affairs Association (UAA)\\
American Political Science Association (APSA)\\
Latin American Studies Association (LASA)\\
American Association of Geographers (AAG) 

    
    \subsection*{Volunteer Work}
    \begin{tablist}
    \item[2020‑2023] $\>$ $\>${}Women Leaders in STEM (US‑Mexico Leaders Network), Mentor
    \item[2018] \tab{}$\>$  $\>$CompileHer (UChicago Tech Capstone), Instructor
    \item[2018] \tab{}$\>$  $\>$Scopeathon (South Side Civic), Community Outreach
    \item[2005] \tab{}$\>$  $\>$Alfabetiza! (ADECO), Instructor and Organizer
    \end{tablist}
    
    \section*{Skills}
    \begin{tablist}
        \item[\textbf{Statistical Analysis and Computation:}] Python, R, STATA, PostgreSQL, Google Cloud Console
        \item[\textbf{Spatial Analysis and GIS:}] GeoDa, QGIS, ArcGIS, PostGIS, Google Earth Engine
        \item[\textbf{General Tools:}] MS Office, LaTeX, Git
        \item[\textbf{Languages:}] Spanish, English, German (A2), French (A1)
    \end{tablist}

\end{document}
